---
title: "Stock Market Visualization Before and After Covid"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    source_code: embed
    css: styles.css
    theme:
      version: 4
      bootswatch: yeti
---

```{r setup, include=FALSE}
library(flexdashboard)
library(quantmod)
library(highcharter)
library(DT)
library(PerformanceAnalytics)
```

# Apple Stock Analysis

Column {data-width=500, .tabset .tabset-fade}
-----------------------------------------------------------------------

### From 2019 to 2022

```{r}
price_aapl <- getSymbols("AAPL", auto.assign = FALSE, from="2019-01-01", to="2022-04-01")
price_aapl_a <- getSymbols("AAPL", auto.assign=FALSE, from="2019-01-01", to="2020-02-01")
price_aapl_b <- getSymbols("AAPL", auto.assign=FALSE, from="2020-02-01", to="2021-06-01")
price_aapl_c <- getSymbols("AAPL", auto.assign=FALSE, from="2021-06-01", to="2022-04-01")
highchart(type="stock") %>% 
  hc_add_series(price_aapl_a, upColor = "#2ECC71 ", color = "#E74C3C") %>% 
  hc_add_series(price_aapl_b, upColor = "#2ECC71 ", color = "#E74C3C") %>% 
  hc_add_series(price_aapl_c, upColor = "#2ECC71 ", color = "#E74C3C") %>% 
  hc_add_series(SMA(na.omit(Cl(price_aapl)),n=50),name="SMA(50)") %>%
  hc_add_series(SMA(na.omit(Cl(price_aapl)),n=200),name="SMA(200)") %>%
  hc_title(text="<b>Apple Price Candle Stick Chart 2019-2022</b>")
```

### Before Covid

```{r}
highchart(type="stock") %>% 
  hc_add_series(price_aapl_a, upColor = "#2ECC71 ", color = "#E74C3C") %>% 
  hc_title(text="<b>Apple Price Candle Stick Chart from 2019-2020 (before Covid)</b>")
```

### During Covid

```{r}
highchart(type="stock") %>% 
  hc_add_series(price_aapl_b, upColor = "#2ECC71 ", color = "#E74C3C") %>% 
  hc_title(text="<b>Apple Price Candle Stick Chart 2020-2021 (during Covid)</b>")
```

### After Covid

```{r}
highchart(type="stock") %>% 
  hc_add_series(price_aapl_c, upColor = "#2ECC71 ", color = "#E74C3C") %>% 
  hc_title(text="<b>Apple Price Candle Stick Chart 2021-2022 (after Covid)</b>")
```

Column {data-width=300}
-----------------------------------------------------------------------

### Apple Highest Stock Price during Covid

```{r}
appl_df_b <- data.frame(price_aapl_b)
appl_high_b <- max(appl_df_b[ ,2])
valueBox(round(appl_high_b, digits = 2),
         caption = "Apple Stock Highest price during Covid",
         color = "#2ECC71",
         icon = "fa-arrow-up")
```

### Apple Lowest Stock Price during Covid

```{r}
appl_df_b <- data.frame(price_aapl_b)
appl_low_b <- min(appl_df_b[ ,3])
valueBox(round(appl_low_b, digits = 2),
         caption = "Apple Stock Lowest price during Covid",
         color = "#CD6155",
         icon = "fa-arrow-down")
```

### Apple Highest Stock price

```{r}
appl_df <- data.frame(price_aapl)
appl_dt <- appl_df[ ,c(1:4)]
appl_high_a <- max(appl_df[,2])
valueBox(round(appl_high_a, digits = 2), 
         caption = "Apple Stock Highest price from 2019 to 2022",
         color = "#2ECC71",
         icon = "fa-arrow-up")
```

### Apple lowest Stock price 

```{r}
appl_low_a <- min(appl_df[,3])
valueBox(round(appl_low_a, digits = 2), 
         caption = "Apple Stock Lowest price from 2019 to 2022",
         color = "#CD6155",
         icon = "fa-arrow-down")
```

### Data table (Search for specific dates)

```{r}
datatable(appl_dt,
          options = list(pageLength = 20, info = FALSE))
```


# JP Morgan Stock Analysis

Column {data-width=500, .tabset .tabset-fade}
-----------------------------------------------------------------------

### From 2019 to 2022

```{r}
price_jpm <- getSymbols("JPM", auto.assign = FALSE, from="2019-01-01", to="2022-04-01")
price_jpm_a <- getSymbols("JPM", auto.assign=FALSE, from="2019-01-01", to="2020-02-01")
price_jpm_b <- getSymbols("JPM", auto.assign=FALSE, from="2020-02-01", to="2021-06-01")
price_jpm_c <- getSymbols("JPM", auto.assign=FALSE, from="2021-06-01", to="2022-04-01")
highchart(type="stock") %>% 
  hc_add_series(price_jpm_a, upColor = "#2ECC71 ", color = "#E74C3C") %>% 
  hc_add_series(price_jpm_b, upColor = "#2ECC71 ", color = "#E74C3C") %>% 
  hc_add_series(price_jpm_c, upColor = "#2ECC71 ", color = "#E74C3C") %>% 
  hc_add_series(SMA(na.omit(Cl(price_jpm)),n=50),name="SMA(50)") %>%
  hc_add_series(SMA(na.omit(Cl(price_jpm)),n=200),name="SMA(200)") %>%
  hc_title(text="<b>JP Morgan Price Candle Stick Chart 2019-2022</b>")
```

### Before Covid

```{r}
highchart(type="stock") %>% 
  hc_add_series(price_jpm_a, upColor = "#2ECC71 ", color = "#E74C3C") %>% 
  hc_title(text="<b>JP Morgan Price Candle Stick Chart from 2019-2020 (before Covid)</b>")
```


### During Covid

```{r}
highchart(type="stock") %>% 
  hc_add_series(price_jpm_b, upColor = "#2ECC71 ", color = "#E74C3C") %>% 
  hc_title(text="<b>JP Morgan Price Candle Stick Chart 2020-2021 (during Covid)</b>")
```


### After Covid

```{r}
highchart(type="stock") %>% 
  hc_add_series(price_jpm_c, upColor = "#2ECC71 ", color = "#E74C3C") %>% 
  hc_title(text="<b>JP Morgan Price Candle Stick Chart 2021-2022 (after Covid)</b>")
```

Column {data-width=300}
-----------------------------------------------------------------------

### JPM Highest Stock Price during Covid

```{r}
jpm_df_b <- data.frame(price_jpm_b)
jpm_high_b <- max(jpm_df_b[ ,2])
valueBox(round(jpm_high_b, digits = 2),
         caption = "JP Morgan Stock Highest price during Covid",
         color = "#2ECC71",
         icon = "fa-arrow-up")
```

### JPM Lowest Stock Price during Covid

```{r}
jpm_df_b <- data.frame(price_jpm_b)
jpm_low_b <- min(jpm_df_b[ ,3])
valueBox(round(jpm_low_b, digits = 2),
         caption = "JP Morgan Stock Lowest price during Covid",
         color = "#CD6155",
         icon = "fa-arrow-down")
```


### JPM Highest Stock price

```{r}
jpm_df <- data.frame(price_jpm)
jpm_dt <- jpm_df[ ,c(1:4)]
jpm_high_a <- max(jpm_df[,2])
valueBox(round(jpm_high_a, digits = 2), 
         caption = "JP Morgan Stock Highest price from 2019 to 2022",
         color = "#2ECC71",
         icon = "fa-arrow-up")
```

### JPM lowest Stock price 

```{r}
jpm_low_a <- min(jpm_df[,3])
valueBox(round(jpm_low_a, digits = 2), 
         caption = "JP Morgan Stock Lowest price from 2019 to 2022",
         color = "#CD6155",
         icon = "fa-arrow-down")
```

### Data table (Search for specific dates)

```{r}
datatable(jpm_dt,
          options = list(pageLength = 20, info = FALSE))
```

# Moderna Stock Analysis

Column {data-width=500, .tabset .tabset-fade}
-----------------------------------------------------------------------

### From 2019 to 2022

```{r}
price_mrna <- getSymbols("MRNA", auto.assign = FALSE, from="2019-01-01", to="2022-04-01")
price_mrna_a <- getSymbols("MRNA", auto.assign=FALSE, from="2019-01-01", to="2020-02-01")
price_mrna_b <- getSymbols("MRNA", auto.assign=FALSE, from="2020-02-01", to="2021-06-01")
price_mrna_c <- getSymbols("MRNA", auto.assign=FALSE, from="2021-06-01", to="2022-04-01")
highchart(type="stock") %>% 
  hc_add_series(price_mrna_a, upColor = "#2ECC71 ", color = "#E74C3C") %>% 
  hc_add_series(price_mrna_b, upColor = "#2ECC71 ", color = "#E74C3C") %>% 
  hc_add_series(price_mrna_c, upColor = "#2ECC71 ", color = "#E74C3C") %>% 
  hc_add_series(SMA(na.omit(Cl(price_mrna)),n=50),name="SMA(50)") %>%
  hc_add_series(SMA(na.omit(Cl(price_mrna)),n=200),name="SMA(200)") %>%
  hc_title(text="<b>Moderna Price Candle Stick Chart 2019-2022</b>")
```

### Before Covid

```{r}
highchart(type="stock") %>% 
  hc_add_series(price_mrna_a, upColor = "#2ECC71 ", color = "#E74C3C") %>% 
  hc_title(text="<b>Moderna Price Candle Stick Chart from 2019-2020 (before Covid)</b>")
```


### During Covid

```{r}
highchart(type="stock") %>% 
  hc_add_series(price_mrna_b, upColor = "#2ECC71 ", color = "#E74C3C") %>% 
  hc_title(text="<b>Moderna Price Candle Stick Chart 2020-2021 (during Covid)</b>")
```

### After Covid

```{r}
highchart(type="stock") %>% 
  hc_add_series(price_mrna_c, upColor = "#2ECC71 ", color = "#E74C3C") %>% 
  hc_title(text="<b>Moderna Price Candle Stick Chart 2021-2022 (after Covid)</b>")
```

Column {data-width=300}
-----------------------------------------------------------------------

### Moderna Highest Stock Price during Covid

```{r}
mrna_df_b <- data.frame(price_mrna_b)
mrna_high_b <- max(mrna_df_b[ ,2])
valueBox(round(mrna_high_b, digits = 2),
         caption = "Moderna Stock Highest price during Covid",
         color = "#2ECC71",
         icon = "fa-arrow-up")
```

### Moderna Lowest Stock Price during Covid

```{r}
mrna_df_b <- data.frame(price_mrna_b)
mrna_low_b <- min(mrna_df_b[ ,3])
valueBox(round(mrna_low_b, digits = 2),
         caption = "Moderna Stock Lowest price during Covid",
         color = "#CD6155",
         icon = "fa-arrow-down")
```


### Moderna Highest Stock price

```{r}
mrna_df <- data.frame(price_mrna)
mrna_dt <- mrna_df[ ,c(1:4)]
mrna_high_a <- max(mrna_df[,2])
valueBox(round(mrna_high_a, digits = 2), 
         caption = "Moderna Stock Highest price from 2019 to 2022",
         color = "#2ECC71",
         icon = "fa-arrow-up")
```

### Moderna lowest Stock price 

```{r}
mrna_low_a <- min(mrna_df[,3])
valueBox(round(mrna_low_a, digits = 2), 
         caption = "Moderna Stock Lowest price from 2019 to 2022",
         color = "#CD6155",
         icon = "fa-arrow-down")
```

### Data table (Search for specific dates)

```{r}
datatable(mrna_dt,
          options = list(pageLength = 20, info = FALSE))
```


# Tesla Stock Analysis

Column {data-width=500, .tabset}
-----------------------------------------------------------------------

### From 2019 to 2022

```{r}
price_tsla <- getSymbols("TSLA", auto.assign = FALSE, from="2019-01-01", to="2022-04-01")
price_tsla_a <- getSymbols("TSLA", auto.assign=FALSE, from="2019-01-01", to="2020-02-01")
price_tsla_b <- getSymbols("TSLA", auto.assign=FALSE, from="2020-02-01", to="2021-06-01")
price_tsla_c <- getSymbols("TSLA", auto.assign=FALSE, from="2021-06-01", to="2022-04-01")
highchart(type="stock") %>% 
  hc_add_series(price_tsla_a, upColor = "#2ECC71 ", color = "#E74C3C") %>% 
  hc_add_series(price_tsla_b, upColor = "#2ECC71 ", color = "#E74C3C") %>% 
  hc_add_series(price_tsla_c, upColor = "#2ECC71 ", color = "#E74C3C") %>% 
  hc_add_series(SMA(na.omit(Cl(price_tsla)),n=50),name="SMA(50)") %>%
  hc_add_series(SMA(na.omit(Cl(price_tsla)),n=200),name="SMA(200)") %>%
  hc_title(text="<b>Tesla Price Candle Stick Chart 2019-2022</b>")
```

### Before Covid

```{r}
highchart(type="stock") %>% 
  hc_add_series(price_tsla_a, upColor = "#2ECC71 ", color = "#E74C3C") %>% 
  hc_title(text="<b>Tesla Price Candle Stick Chart from 2019-2020 (before Covid)</b>")
```

### During Covid

```{r}
highchart(type="stock") %>% 
  hc_add_series(price_tsla_b, upColor = "#2ECC71 ", color = "#E74C3C") %>% 
  hc_title(text="<b>Tesla Price Candle Stick Chart 2020-2021 (during Covid)</b>")
```

### After Covid

```{r}
highchart(type="stock") %>% 
  hc_add_series(price_tsla_c, upColor = "#2ECC71 ", color = "#E74C3C") %>% 
  hc_title(text="<b>Tesla Price Candle Stick Chart 2021-2022 (after Covid)</b>")
```

Column {data-width=300}
-----------------------------------------------------------------------

### Apple Highest Stock Price during Covid

```{r}
tsla_df_b <- data.frame(price_tsla_b)
tsla_high_b <- max(tsla_df_b[ ,2])
valueBox(round(tsla_high_b, digits = 2),
         caption = "Tesla Stock Highest price during Covid",
         color = "#2ECC71",
         icon = "fa-arrow-up")
```

### Apple Lowest Stock Price during Covid

```{r}
tsla_df_b <- data.frame(price_tsla_b)
tsla_low_b <- min(tsla_df_b[ ,3])
valueBox(round(tsla_low_b, digits = 2),
         caption = "Tesla Stock Lowest price during Covid",
         color = "#CD6155",
         icon = "fa-arrow-down")
```


### Apple Highest Stock price

```{r}
tsla_df <- data.frame(price_tsla)
tsla_dt <- tsla_df[ ,c(1:4)]
tsla_high_a <- max(tsla_df[,2])
valueBox(round(tsla_high_a, digits = 2), 
         caption = "Tesla Stock Highest price from 2019 to 2022",
         color = "#2ECC71",
         icon = "fa-arrow-up")
```

### Apple lowest Stock price 

```{r}
tsla_low_a <- min(tsla_df[,3])
valueBox(round(tsla_low_a, digits = 2), 
         caption = "Tesla Stock Lowest price from 2019 to 2022",
         color = "#CD6155",
         icon = "fa-arrow-down")
```

### Data table (Search for specific dates)

```{r}
datatable(tsla_dt,
          options = list(pageLength = 20, info = FALSE))
```


# Amazon Stock Analysis

Column {data-width=500, .tabset .tabset-fade}
-----------------------------------------------------------------------

### From 2019 to 2022

```{r}
price_amzn <- getSymbols("AMZN", auto.assign = FALSE, from="2019-01-01", to="2022-04-01")
price_amzn_a <- getSymbols("AMZN", auto.assign=FALSE, from="2019-01-01", to="2020-02-01")
price_amzn_b <- getSymbols("AMZN", auto.assign=FALSE, from="2020-02-01", to="2021-06-01")
price_amzn_c <- getSymbols("AMZN", auto.assign=FALSE, from="2021-06-01", to="2022-04-01")
highchart(type="stock") %>% 
  hc_add_series(price_amzn_a, upColor = "#2ECC71 ", color = "#E74C3C") %>% 
  hc_add_series(price_amzn_b, upColor = "#2ECC71 ", color = "#E74C3C") %>% 
  hc_add_series(price_amzn_c, upColor = "#2ECC71 ", color = "#E74C3C") %>% 
  hc_add_series(SMA(na.omit(Cl(price_amzn)),n=50),name="SMA(50)") %>%
  hc_add_series(SMA(na.omit(Cl(price_amzn)),n=200),name="SMA(200)") %>%
  hc_title(text="<b>Amazon Price Candle Stick Chart 2019-2022</b>")
```


### Before Covid

```{r}
highchart(type="stock") %>% 
  hc_add_series(price_amzn_a, upColor = "#2ECC71 ", color = "#E74C3C") %>% 
  hc_title(text="<b>Amazon Price Candle Stick Chart from 2019-2020 (before Covid)</b>")
```


### During Covid

```{r}
highchart(type="stock") %>% 
  hc_add_series(price_amzn_b, upColor = "#2ECC71 ", color = "#E74C3C") %>% 
  hc_title(text="<b>Amazon Price Candle Stick Chart 2020-2021 (during Covid)</b>")
```


### After Covid

```{r}
highchart(type="stock") %>% 
  hc_add_series(price_amzn_c, upColor = "#2ECC71 ", color = "#E74C3C") %>% 
  hc_title(text="<b>Amazon Price Candle Stick Chart 2021-2022 (after Covid)</b>")
```

Column {data-width=300}
-----------------------------------------------------------------------

### Amazon Highest Stock Price during Covid

```{r}
amzn_df_b <- data.frame(price_amzn_b)
amzn_high_b <- max(amzn_df_b[ ,2])
valueBox(round(amzn_high_b, digits = 2),
         caption = "Amazon Stock Highest price during Covid",
         color = "#2ECC71",
         icon = "fa-arrow-up")
```

### Amazon Lowest Stock Price during Covid

```{r}
amzn_df_b <- data.frame(price_amzn_b)
amzn_low_b <- min(amzn_df_b[ ,3])
valueBox(round(amzn_low_b, digits = 2),
         caption = "Amazon Stock Lowest price during Covid",
         color = "#CD6155",
         icon = "fa-arrow-down")
```


### Amazon Highest Stock price

```{r}
amzn_df <- data.frame(price_amzn)
amzn_dt <- amzn_df[ ,c(1:4)]
amzn_high_a <- max(amzn_df[,2])
valueBox(round(amzn_high_a, digits = 2), 
         caption = "Amazon Stock Highest price from 2019 to 2022",
         color = "#2ECC71",
         icon = "fa-arrow-up")
```

### Apple lowest Stock price 

```{r}
amzn_low_a <- min(amzn_df[,3])
valueBox(round(amzn_low_a, digits = 2), 
         caption = "Amazon Stock Lowest price from 2019 to 2022",
         color = "#CD6155",
         icon = "fa-arrow-down")
```

### Data table (Search for specific dates)

```{r}
datatable(amzn_dt,
          options = list(pageLength = 20, info = FALSE))
```

# Comparison

Column {.tabset}
-----------------------------------------------------------------------

### Before Covid

```{r}
highchart(type="stock") %>% 
  hc_add_series(Cl(price_aapl_a), name="AAPL") %>% 
  hc_add_series(Cl(price_jpm_a), name="JPM") %>%
  hc_add_series(Cl(price_mrna_a), name="MRNA") %>%
  hc_add_series(Cl(price_tsla_a), name="TSLA") %>%
  # hc_add_series(Cl(price_amzn_a), name="AMZN") %>%
  hc_title(text="<b>Apple vs JP Morgan vs Moderna vs Tesla vs Amazon Closing Price before Covid</b>")
```

### During Covid

```{r}
highchart(type="stock") %>% 
  hc_add_series(Cl(price_aapl_b), name="AAPL") %>% 
  hc_add_series(Cl(price_jpm_b), name="JPM") %>%
  hc_add_series(Cl(price_mrna_b), name="MRNA") %>%
  hc_add_series(Cl(price_tsla_b), name="TSLA") %>%
  # hc_add_series(Cl(price_amzn_b), name="AMZN") %>%
  hc_title(text="<b>Apple vs JP Morgan vs Moderna vs Tesla vs Amazon Closing Price during Covid</b>")
```

### After Covid

```{r}
highchart(type="stock") %>% 
  hc_add_series(Cl(price_aapl_c), name="AAPL") %>% 
  hc_add_series(Cl(price_jpm_c), name="JPM") %>%
  hc_add_series(Cl(price_mrna_c), name="MRNA") %>%
  hc_add_series(Cl(price_tsla_c), name="TSLA") %>%
  # hc_add_series(Cl(price_amzn_c), name="AMZN") %>%
  hc_title(text="<b>Apple vs JP Morgan vs Moderna vs Tesla Closing Price after Covid</b>")
```

## {-}

### Returns

```{r}
# Calculate the stocks return
return_appl <- dailyReturn(Cl(price_aapl_b))
return_jpm <- dailyReturn(Cl(price_jpm_b))
return_mrna <- dailyReturn(Cl(price_mrna_b))
return_tsla <- dailyReturn(Cl(price_tsla_b))
return_amzn <- dailyReturn(Cl(price_amzn_b))

# Combine the returns as one data frame
returns <- data.frame(return_appl,return_jpm,return_mrna,return_tsla,return_amzn)
names(returns) <- c("return_appl","return_jpm","return_mrna","return_tsla","return_amzn")
returns <- as.xts(returns)

# Plot the returns
charts.PerformanceSummary(returns,main="Daily Return \nApple vs JP Morgan vs Moderna vs Tesla vs Amazon \nduring Covid")
```

